Untrusted B2B Collaboration using the Blockchain

### 2018-07-25 paper/paper.tex
clarify event throws, correct a phrase

\subsection{Prior Work on Business Processes on the Blockchain}
In \cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
They describe a contract architecture, where a factory contract is responsible for deploying instance contracts for each process instance.
They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
In order to achieve BPMN-to-Solidity compilation, they describe translation rules to transform BPMN elements to Solidity code.
%TODO highlight lack of access right explanation and problem of central contract?

@@

%basic understanding/ intuition
%-> make orchestration possible

% Decentralized contracts vs. central monitor
% Engine on chain vs. message channel

%use one contuous example

%visualizations !!

@@

Every organization provides an interface of their public process in an \emph{instance contract}.
Additionally, \emph{factory contracts} manage these instance contracts and \emph{access contracts} are used for rights management.
The contract structure will be described in detail in the following sections.
We assume that all participating organizations use a process engine to execute their private processes.
When a throw event is triggered within a process engine, a \emph{throw event function} is called on an instance contract and the corresponding \emph{catch event function} is called on the instance contract of the organization responsible for catching the event.
Thus, the public processes of all organizations are recorded on the blockchain.

@@

%TODO correctly show that the address is passed instead of using msg.sender
When a throw event is triggered in the process engine of organization $A$, the corresponding \emph{throw event function} is called on the instance contract of the collaboration partner $B$.
In the instance contract of $A$ an authorization is performed by looking up the sender address in the access contract of $A$.
If this check is successful, the \emph{catch event function} is called on the partner instance contract of $B$.
In the instance contract of $B$ there is another authorization against the access contract of $A$.
This ensures that both sides can be confident, that the throw event was triggered by an authorized person who belongs to organization $A$.
If this check was also successful, an event is emitted to the blockchain.
This will be detected by the trigger of $B$ and passed to the process engine.
Thus, a message was sent from $A$ to $B$ via the blockchain and an audit trail was created.
An example can be seen in the sequence diagram in Figure \ref{fig:event_sending}.

>>>>

% TODO search for more papers, such as Optimized execution of business processes on blockchain
\subsection{Prior Work on Business Processes on the Blockchain}
In \cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
They describe a contract architecture, where a factory contract is responsible for deploying instance contracts for each process instance.
They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
In order to achieve BPMN-to-Solidity compilation, they describe translation rules to transform BPMN elements to Solidity code.
%TODO highlight lack of access right explanation and problem of central contract?

@@

\section{Requirements}
% refer to presentation here
% TODO Vielleicht könnt ihr ganz am Anfang einen Überblick geben was das System erfüllen muss, wie das geschieht erklärt ihr dann in den  Unterkapiteln

@@

Every organization provides an interface of their public process in an \emph{instance contract}.
Additionally, \emph{factory contracts} manage these instance contracts and \emph{access contracts} are used for rights management.
The contract structure will be described in detail in the following sections.
We assume that all participating organizations use a process engine to execute their private processes.
When a throw event is triggered within a process engine, the process engine calls the \emph{throw event function} on an instance contract and the corresponding \emph{catch event function} is called on the instance contract of the organization responsible for catching the event.
Thus, all communication between organizations is recorded on the blockchain.

@@

%TODO correctly show that the address is passed instead of using msg.sender
When a throw event is triggered in the process engine of organization $A$, the process engine of $A$ calls the corresponding \emph{throw event function} on the instance contract of organization $A$.
In the instance contract of $A$ an authorization is performed by looking up the sender address in the access contract of $A$.
If this check is successful, the \emph{catch event function} is called on the partner instance contract of $B$.
In the instance contract of $B$ there is another authorization against the access contract of $A$.
This ensures that both sides can be confident, that the throw event was triggered by an authorized person who belongs to organization $A$.
If this check was also successful, an event is emitted to the blockchain.
This will be detected by the trigger of $B$ and passed to the process engine.
Thus, a message was sent from $A$ to $B$ via the blockchain and an audit trail was created.
An example can be seen in the sequence diagram in Figure \ref{fig:event_sending}.
